\documentclass{article}
\usepackage[utf8]{inputenc}


\title{Monitoring Parsl Workflows}
\author{Connor Pigg and Dr. Daniel S. Katz}
\date{July 2018}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}

\begin{document}

\maketitle

\section{Abstract}
\input{abstract.tex}
\pagebreak

\section{Introduction}
\input{intro.tex}

\section{Background and Significance}
Workflow software is used by researchers and projects to automate the execution of and transition between actions that typically occur in any given process.
Parsl empowers users to utilize the parallel capabilities of computers through implicit parallelization of these workflows.
This speeds up the execution and reduces human errors in the process.
These tools also give users the ability to audit, publish, and debug their workflows improving their quality and reproducibility.
To further enable these specific uses of workflow tools, this project is adding monitoring to Parsl.

Parsl's decision to include monitoring at such a relatively young age conveys the importance of monitoring to users of such software.

\section{Potential Benefits}
These monitoring capabilities will improve the user's understanding of the behavior of their workflow.
This allows the detection of abnormalities, errors, and performance of their workflow.
This information improves the efficiency at which a user can solve workflow problems and achieve results.

Monitoring should also increase adoption of automated workflows.
Increased adoption would improve the productivity of these users and empower these users to contribute more to their communities.

\section{Methods}
\input{body.tex}

\section{Conclusion}
\input{conclusion.tex}

\bibliographystyle{plain}
\bibliography{references}
\end{document}
